\thetitle

### 2020-11-21 writing/results.tex
Replace bt-lengths-table with version aggregating over all benchmarks

\begin{figure*}
  \centering
  \includegraphics[width=0.95\textwidth]{./plots/bt-lengths-table}
  \caption{Programmer effort: Each cell depicts the distribution of trail
  lengths for a given mode and a benchmark's mutants starting from trails
  of length 0.}
  \label{fig:effort-table}
\end{figure*}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{./plots/bt-lengths-table}
  \caption{Programmer effort: Each plot depicts the distribution of trail
  lengths for a given mode across all benchmarks, starting from trails
  of length 0.}
  \label{fig:effort-table}
\end{figure}
